---
title: "math250_nov5_ChristianJimenez"
author: "Christian Jimenez"
format: html
embed-resources: true
---
```{r, echo=FALSE, message =FALSE}
library(tidyverse)
library(ISLR2)
data("Carseats")
```

# Problem 1

The first two problems in this set refer to the ISLR2::Carseats, does this data provide evidence against the company’s claim that the average price of their own seats is $110? Follow all best practices from class, including hypotheses, a relevant visualization, and a conclusion in non-technical language.

```{r}
t.test(Carseats$Price, mu = 110)
```

$H_0: \mu = 110$  $H_1: \mu \neq 110$

Testing whether the average price of Carseats is $110.



```{r}
ggplot(Carseats, aes(y = Price)) +
  geom_boxplot(fill = "lightblue")+
    geom_hline(yintercept = 110, color = "red", linetype = "dashed")+  theme_minimal()
  
  

```

## Conclusion 

After our test and box plot we can clearly see the dashed red line showing the average price claim of $110, which  is not true. Companies are charging noticeably more on average. Avergaing more around $115 - $116 range.


# Problem 2
Compute a level 90% confidence interval for the mean competitor price in the population from which this sample is drawn. What is the sample mean? What is the margin of error?

```{r}
t.test(Carseats$CompPrice, conf.level = 0.90)
```
```{r}
M.E = (126.2391-123.7109)/2
M.E 
```

The sample mean of the `CompPrice` column is $124.98, with the confidence interval ranging from $123.71 to $126.24. This shows our margin of error at a 90% confidence interval is $1.26 indicating that we are 90% confident the true mean falls within this interval.

#Problem 3
create a table with counts of penguin species and home islands in the penguins set. Include marginal counts in your table.
```{r, message=FALSE}
data("penguins")

```

```{r}
table = table(penguins$species, penguins$island )
addmargins(table)
```

